---
title: "Alcohol vs Seat choice"
author: "Miguel Avila"
date: "Fall 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question 
Is there a difference between the alcohol consumed between the row you choose to sit in?

## Method

$H_0$: There is no difference between the alcohol consumed between the row you choose to sit in.  
$H_A$: There is a difference between the alcohol consumed between the row you choose to sit in.  

Alcohol consumed~numerical
Seated row~categorical
Thus we use the helper file Numerical~Cat

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The plot shows that the back row of seats consumes the most alcohol, followed by the middle row, and lastly the front row consumes the least.

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

The numerical shows that the back row of seats consume about three times the amount of alcohol that the front row of seats consume.

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

```{r}
plot(TukeyHSD(model1))
```

## Conclusions


